Title Goes Here

### 2020-02-25 paper/paper.tex
Restored 'TODO' about Oxford brackets
Expand introduction with motivation, add list of contributions and remove 'Structure of paper' section

Embedded domain specific languages (EDSLs) have long been a useful and effective
technique for constructing reusable tools for writing programs for a variety of
different problem domains. Haskell is a language which is particularly
well-suited to EDSLs due to its lazy evaluation, first-class functions and
lexical closures.

@@

\subsection{Structure of the Paper}

\begin{itemize}
  \item In section 3, an EDSL representation of pattern matching will be
    introduced.
  \item Sections 4 and 5 will discuss techniques for representing tail recursion
    and lambdas (respectively) in an EDSL. The tail recursion transformation
    does not depend on the rest of the EDSL and can be used separately from it.
  \item Section 6 provides an implementation of \ttt{abs} which interprets an EDSL
    expression under the "standard" semantics (that is, applying this implementation
    to the result of the Core transformation will result in a program that behaves exactly
    the same as the original, untransformed, program).
  \item Section 7 describes the general control flow and specific syntactic
    transformations of the Core plugin.
\end{itemize}

\subsection{Translation Example} % TODO: 
\begin{tcolorbox}
  \textbf{TODO}: Does it make sense for this to be a subsection of the intro?
\end{tcolorbox}

@@

@@

\clearpage
\subsection{Syntactic Transformations of the Core Plugin}

% \begin{tcolorbox}
%   \textbf{TODO}: Does this subsection use Oxford brackets in an appropriate way?
% \end{tcolorbox}

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &\rewrites \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

@@

Note that:
\begin{itemize}
  \item The tail recursion transformation given by $D$ and $T_{\ttt{f}}$ is completely independent of the \ttt{E} type and the transformations associated to the \ttt{E} type. As a result, the tail recursion transformation can be used on its own.

>>>>

Embedded domain specific languages (EDSLs) have long been an effective
technique for constructing reusable tools for working in a variety of
different problem domains. Haskell is a language which is particularly
well-suited to EDSLs due to its lazy evaluation, first-class functions and
lexical closures.

Despite these advantages Haskell provides for creating EDSLs, there are a few
constructs which have often proved illusive to embed in an EDSL. One prominent
example is that of a \ttt{case} expression. Pattern matching is a convenient way
to implement control flow structures and to view components of data structures,
so it is frequently a desirable feature for many EDSLs.

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda.

The following contributions are made by this paper:

\begin{itemize}
\item A representation of pattern matching in a Haskell EDSL (Section 3)
\item Representations of tail recursion (Section 4) and lambdas (Section 5) in
  the EDSL. We will see that lambdas become easier to implement once pattern
  matching and tail recursion already have EDSL representations.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section 7)
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section 6).
\end{itemize}

@@

\subsection{Translation Example}
\begin{tcolorbox}
  \textbf{TODO}: Does it make sense for this to be a subsection of the intro?
\end{tcolorbox}

@@

If we postcompose with \ttt{runSumMatch}, we get:

\begin{lstlisting}
runSumMatch . abs :: E (SumMatch a b) -> (a -> b)
\end{lstlisting}

@@

\clearpage
\subsection{Syntactic Transformations of the Core Plugin}
\begin{tcolorbox}
  \textbf{TODO}: Should we use Oxford brackets here? Maybe a bit unusual, but we are operating syntactically and mapping from \ttt{a} to \ttt{E a} (could \ttt{E a} be considered an "intermediary" semantic domain?).
\end{tcolorbox}
\vspace*{-0.6cm}
\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &\rewrites \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

@@

Note that:
\begin{itemize}
  \item The tail recursion transformation given by $D$, $T'_{\ttt{f}}$ and $T_{\ttt{f}}$ is completely independent of the \ttt{E} type and the transformations associated to the \ttt{E} type. As a result, the tail recursion transformation can be used on its own.
